The effects of binarity on planet occurrence rates measured by transit surveys

### 2017-12-16 paper/main.tex
paper: further figure edits
paper: updating text (WIP)

\newcommand{\pp}{\mathcal{P}}
\newcommand{\ps}{\mathcal{S}}
\renewcommand{\a}{_{\rm a}}
\newcommand{\s}{_{\rm s}}
\begin{document}

@@

A group of astronomers wants to measure the mean number of planets of a 
certain type per star of a certain type.
Ignoring stellar multiplicity, they perform a signal-to-noise limited transit 
survey, and detect a set of planets that appear to be of the desired class.
They then choose the stars (among those initially surveyed) around which the 
planets of interest appeared to be searchable.
Correcting for the geometric transit probability $p_{\rm tra}$, they report an 
apparent rate density,
\begin{equation}
\Gamma\a(\pp\a, \ps\a) = \frac{N_{\rm det}(\pp\a, \ps\a)}{N_{\rm s,a}(\pp\a, 
    \ps\a)} \times \frac{1}{p_{\rm tra}(\pp\a, \ps\a)}.
\label{eq:wouldnt_it_be_nice}
\end{equation}
where $\pp\a$, $\ps\a$ are the apparent planetary and stellar parameters, 
respectively.
Here $N_{\rm det}(\pp\a, \ps\a)$ is the number of 
detected planets with parameters $\pp\a,\ps\a$, per unit $\pp\a$ and $\ps\a$. 
The quantity $N_{\rm s,a}(\pp\a, \ps\a)$ is the number of unresolved 
point-sources on the sky the appear to be searchable.

@@

Here we focus on problems that arise from the fact that many stars exist in 
multiple star systems.
For simplicity, we consider only binaries, and we assume that they are all 
spatially unresolved.

@@

Outside of astrophysical differences, there are observational biases for every 
term in Eq.~\ref{eq:wouldnt_it_be_nice}.
There are errors in $N_{\rm det}$ due to planet radius 
misclassification.
There are errors in $N_{{\rm s,a}}$ because a given point on the sky
There are errors in $p_{\rm tra}(\pp\a,\ps\a)$ because stars in binaries may 
have different masses and radii than assumed in the single-star case.
Binarity might also affect the observers' ability to correctly select 
searchable stars (but see Sec.~\ref{sec:model_1} for discussion of why this is 
a second-order effect).

Finally, there are errors in $p_{\rm det}$ because detection efficiencies 
for planets orbiting single stars, primaries, and secondaries are all 
different.

@@

To gain intuition for the many observational biases at play,
we consider a set of idealized transit surveys:
\begin{itemize}
    \item Model \#1: fixed stars, fixed planets, twin binaries;
    \item Model \#2: fixed planets and primaries, varying secondaries;
    \item Model \#3: fixed primaries, varying planets and secondaries.
\end{itemize}
We define our terminology in Sec.~\ref{sec:definitions}, and present
our transit survey models in Secs.~\ref{sec:model_1}-\ref{sec:model_3}, where 
each subsection corresponds to a model listed above.
We interpret these calculations throughout, and in 
Sec.~\ref{sec:discussion} connect them to topical questions in 
the interpretation of transit survey occurrence rates.
In particular, we mention the ``hot Jupiter rate discrepancy'', the relevance 
towards measurements of $\eta_\oplus$, and the implications for detailed 
study of \citet{fulton_california-_2017}'s recently discovered ``valley''.
We conclude in Sec.~\ref{sec:conclusion}

@@

\section{Definitions}
\label{sec:definitions}
We define the occurrence rate density, $\Gamma$, as the expected number of 
planets per star per bin of planetary or stellar phase space.
Since we will mainly be concerned with the rate density's dependence on 
planetary radii $r$, we write
\begin{equation}
\Gamma(r) = \frac{{\rm d}\Lambda}{{\rm d}r},
\label{eq:rate_density_defn}
\end{equation}
where $\Lambda$ is the occurrence rate.
In this notation, ``the occurrence rate of planets of a particular size'' 
translates to an integral of Eq.~\ref{eq:rate_density_defn}, evaluated over a 
radius interval.

The above definition implicitly marginalizes the rate density over stellar 
multiplicity.
In this study we only consider single and binary star systems.
For a selected population of stars and planets, the rate density is then 
a weighted sum of rate densities for each system type:
\begin{equation}
N_{\rm tot} \Gamma(r) =
N_0 \Gamma_0(r) +
N_1 \Gamma_1(r) +
N_2 \Gamma_2(r),
\label{eq:rate_density_marginalized}
\end{equation}
where $i=0$ corresponds to single stars, $i=1$ to primaries of 
binaries, and $i=2$ to secondaries of binaries.
$N_{\rm tot} = \sum_i N_i$ is the total number of selected stars, and 
$N_0,N_1,N_2$ are the number of selected single stars, primaries, and 
secondaries.
Since each selected binary system contributes both a 
primary and secondary star, $N_1=N_2$.
This redundancy in our notation will later prove its use.

Finally, it is helpful to write 
$\Gamma_i(r)$, the rate density for each type of star, as the product of a 
shape function and a constant:
\begin{equation}
\Gamma_i(r) = \frac{{\rm d}\Lambda_i}{{\rm d}r} = Z_i p_i(r),
\quad {\rm for}\ i\in\{0,1,2\}.
\label{eq:rate_density_shape}
\end{equation}
The shape function is normalized to unity.
The $Z_i$'s can be interpreted as each system type's occurrence rate 
$\Lambda_i$, integrated over all planetary radii.
They are equivalent to the number of planets per single star, primary, or 
secondary.

@@

Since the effects of binarity are most pronounced when the two components are 
similar, we begin by considering a universe in which all planets are 
identical, and all stars are identical except that some fraction of them exist 
in binaries.

Expressed mathematically, from Eqs.~\ref{eq:rate_density_marginalized}
and~\ref{eq:rate_density_shape} the occurrence rate density at a planet radius 
$r$ can be written
\begin{equation}
\Gamma(r) = \delta(r_p) \times
\frac{
    N_0 Z_0 +
    N_1 Z_1 +
    N_2 Z_2
}{N_{\rm tot}},
\label{eq:model_1_rate_density}
\end{equation}
where $\delta(r_p)$ is the Dirac delta function, zero except at the true 
planet radius, $r_p$.
The occurrence rate over any interval that includes $r_p$ is then
\begin{equation}
\Lambda|_{r_p} = \frac{
    N_0 Z_0 +
    N_1 Z_1 +
    N_2 Z_2 
}{N_{\rm tot}},
\label{eq:model_1_rate}
\end{equation}
and the rate is zero over intervals that do not include $r_p$.

We return to our group of binarity-ignoring astronomers. They do 
not know the true rate density~--~they would like to discover it!
In their signal-to-noise limited transit survey, they select stars 
that they think can yield transit detections.
Since the noise is Poissonian, they assume
\begin{equation}
\frac{{\rm signal}}{{\rm noise}}
\propto \frac{(r/R)^2}{F^{-1/2}}
\propto F^{1/2}
\propto L_{\rm sys}^{1/2} d^{-1}, \quad ({\rm incorrectly\ assumed})
\end{equation}
for $R$ the constant stellar radius, $F$ the photon flux, $L_{\rm sys}$ the 
luminosity of a system, and $d$ its distance from us.
At fixed planet radius, semimajor axis, stellar radius, and stellar luminosity,
a constant signal-to-noise floor yields a maximum detectable 
distance~\citep{pepper_using_2003,pepper_searching_2005}.
The maximum distance out to which our binarity-ignoring astronomers 
select stars, $d_{\rm sel}$, thus scales as $L_{\rm sys}^{1/2}$.

The single stars have luminosity $L_1$, and the twin binaries have luminosity 
$2L_1$.
Thus the twin binaries are selected out to a distance $\sqrt{2}$ times 
that of single stars.
This is a bad move, because the transit signal for any planet in a 
twin binary will be diluted by a factor of two:
\begin{equation}
\frac{{\rm signal}}{{\rm noise}}
\propto \frac{\mathcal{D} (r/R)^2}{F^{-1/2}}
\propto \mathcal{D} F^{1/2}
\propto \mathcal{D} L_{\rm sys}^{1/2} d^{-1}, \quad ({\rm true})
\label{eq:snr_true}
\end{equation}
where the dilution is $\mathcal{D} \equiv L_{\rm host}/L_{\rm sys}$, for 
$L_{\rm host}$ the the planet host's luminosity.
This means that the true maximum searchable distance for binaries, $d_{\rm 
    det}$, is $1/\sqrt{2}$ times that of single stars.
The situation is illustrated in Fig.~\ref{fig:model_1_volumes}: only one in 
eight selected stars in binaries are truly searchable.

@@

\paragraph{What do the observers ignoring binarity infer?} 
The binarity-ignoring observers assume that all points on the sky with flux 
above some minimum are searchable.
They correct their assumed number of searchable stars for the transit 
probability.
As a function of apparent radius, they then report an apparent rate density of
\begin{equation}
\Gamma_a(r_a) = 
\delta(r_p) Z_0 \frac{N_0}{N_0+N_1}  +
\delta\left(\frac{r_p}{\sqrt{2}}\right) 
(Z_1 p_{{\rm det},1} + Z_2 p_{{\rm det},2}) \frac{N_1}{N_0+N_1},
\label{eq:model_1_apparent_rate_density}
\end{equation}
where $p_{{\rm det},1}$ ($p_{{\rm det},2}$) is the probability that a selected 
primary (secondary) is searchable.
In this example, $p_{{\rm det},1}=p_{{\rm det},2}=1/8$; the detection 
efficiency is the ratio of the searchable to selected volumes.

The true rate density (Eq.~\ref{eq:model_1_rate_density}) and the
apparent rate density (Eq.~\ref{eq:model_1_apparent_rate_density})
differ in that
\begin{enumerate}
    \item The total number of selected stars, $N_{\rm tot} = N_0+N_1+N_2$, was 
    miscounted.
    %
    \item The detection efficiency was incorrectly assumed to be $1$ for all 
    selected stars. In reality, only one in eight binaries were searchable.
    %
    \item The inferred radii in binary systems are all $\sqrt{2}$ too small.
\end{enumerate}

To assess the severity of these errors, we need to make assumptions about the 
stellar and planetary populations.
The important quantity for the stellar population is $N_1/N_0$, the ratio of 
selected primaries (or binaries) to singles. We can define
\begin{align}
\mu \equiv \frac{N_1}{N_0} &=
\frac{n_b}{n_s} \left(\frac{d_{\rm sel,b}}{d_{\rm sel,s}}\right)^3 = 
\frac{{\rm BF}}{1-{\rm BF}} (1+\ell)^{3/2},
\label{eq:mu_definition}
\end{align}
where $n_b$ and $n_s$ are the number density of binaries and singles in a 
volume limited sample, and the maximum selected distance for binary and single 
systems are $d_{\rm sel,b}$ and $d_{\rm sel,s}$.
The light ratio $\ell$ is defined relative to the primary, so that
$L_{\rm sys} = L_1(1+\ell)$.
The binary fraction in a volume limited sample is ``{\rm BF}''.
For instance, \citet{raghavan_survey_2010} found a multiplicity 
fraction\footnote{
    The binary fraction is the fraction of systems in a volume-limited sample 
    that are binary. It is equivalent to the multiplicity fraction if there 
    are no triple, quadruple, or higher order multiples. In that case, ${\rm 
        BF} = n_b / (n_s+n_b)$.
} of 0.44 for primaries with masses from $0.7M_\odot$ to $1.3M_\odot$. 
``Twin binaries'' are perhaps 10-20\% of the binaries in a volume-limited 
sample, depending on how ``twin'' is defined.
Thus a representative twin binary fraction for this model is ${\rm BF}\approx 
0.05$-$0.1$.

Further, we need to assume knowledge of the true number of planets per 
single, primary, and secondary star ($Z_0,Z_1,$ and $Z_2$).
Taking $Z_0=Z_1=Z_2=1/2$, we plot the resulting occurrence rates as a function 
of planet radius in Fig.~\ref{fig:occ_rate_model_1}.
Though it is impossible for an observer to isolate any one of binarity's 
biases without also addressing the others, mathematically it is simply a 
matter of modifying the appropriate terms in 
Eq.~\ref{eq:model_1_apparent_rate_density}.
The resulting rates are also shown in 
Fig.~\ref{fig:occ_rate_model_1}, and demonstrate how each 
error individually affects the overall inferred rate.

\begin{figure}[!tb]
    \begin{center}
        \includegraphics[width=.6\textwidth]{figures/occ_rate_vs_radius_model_1_brokenx.pdf}
    \end{center}
    \vspace{-0.5cm}
    \caption{
        Inferred occurrence rates over $0.01r_\oplus$ bins in planet 
        radius,for Model \#1.
        This model has fixed stars, fixed planets, and twin binaries. 
        Further, a twin binary fraction of ${\rm BF}=0.1$ is assumed, and all 
        planets are {\bf TODO}.
        If the true planet radius is $r_p$, all planets detected in binaries 
        will have apparent radii $r_a = r_p/\sqrt{2}$.
    }
    \label{fig:occ_rate_model_1}
\end{figure}

\paragraph{Correction to inferred rate density and inferred rate}

We define a rate density correction factor, $X_\Gamma$, as the ratio of the 
apparent to true rate densities:
\begin{equation}
X_\Gamma \equiv \frac{\Gamma_a}{\Gamma}.
\end{equation}
This correction factor can be a function of whatever parameters $\Gamma_a$ and 
$\Gamma$ depend on; in this study, the planet radius is most relevant.

If we continue assuming that the number of planets per single, primary, and 
secondary star are equal ($Z_0=Z_1=Z_2$), we find a rate density correction 
factor at the true planet radius of
\begin{equation}
X_\Gamma(r_p) = \frac{1}{1+\mu},
\label{eq:Z_eq_model_1_correction}
\end{equation}
This yields a correction of 0.76 if ${\rm BF}=0.1$, and 0.87 if ${\rm 
    BF}=0.05$.
Rephrasing the result, if the twin binary fraction were 
$(2^{3/2}+1)^{-1}\approx 0.26$, then the apparent rate would be half the true 
rate.
Fortunately, in most contexts the twin binary fraction is not that high.

An alternative assumption is that secondaries do not host planets. In that 
case, $Z_0=Z_1$, and $Z_2=0$. The correction to the rate density at the true 
planet radius becomes
\begin{equation}
X_\Gamma(r_p) = \frac{1+2\mu}{(1+\mu)^2}.
\end{equation}
This evaluates to 0.94 if ${\rm BF}=0.1$, and 0.98 if ${\rm BF}=0.05$.
While it is hard to justify the assumption that secondaries are planet-less, 
it is worth noting that $\Gamma_a/\Gamma$ is sensitive to the relative number 
of planets per single, primary, and secondary.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Model \#2: fixed planets and primaries, varying secondaries}
\label{sec:model_2}

\begin{figure}[!tb]
    \centering
    \includegraphics[width=0.6\textwidth]{figures/mass_ratio_distribution.pdf}
    \caption{
        The mass ratio distribution for a magnitude-limited sample of 
        binary stars, in which the underlying volume-limited distribution is 
        uniform (qualitatively similar to {\it 
            e.g.},~\citet{raghavan_survey_2010}'s Fig.~16).
        The entire bias can be understood analytically 
        (Eq.~\ref{eq:Malmquist_bias}).
    }
    \label{fig:q_distribn_mag_limited}
\end{figure}

Our binary-twin model provides a simple estimate of binarity's systematic 
effects, but perhaps it is too simple.
We begin introducing realism by first letting the light ratio $\ell = L_2/L_1$ 
vary across the binary population.
It does so because the underlying mass ratio $q=M_2/M_1$ varies.
We keep the primary mass fixed as $M_1$, which is also the mass of all single 
stars.

We parametrize the distribution of binary mass ratios in a volume-limited 
sample as a power law: $p(q)\propto q^\beta$.
For binaries with solar-type primaries\footnote{
    \citet{duchene_stellar_2013}, fitting all the multiple systems of 
    \citet{raghavan_survey_2010}'s Fig 16, find $\beta = 0.28\pm0.05$ for 
    $0.7<M_\star/M_\odot<1.3$.
    Examining only the binary systems of \citeauthor{raghavan_survey_2010}'s 
    Fig 
    16, the distribution seems (by eye) to be roughly uniform, $\beta \approx 
    0$, 
    except for an excess of twin binaries with $q\approx 1$, and an obvious 
    lack of $q<0.1$ stellar companions.
}, $\beta$ is probably between 0 and 0.3.
We further assume that stars are a one-parameter family, $R \propto M \propto 
L^{1/\alpha}$, so that a drawn value of $q$ determines everything about a 
secondary.

>>>>

\newcommand{\pp}{\mathcal{P}}
\newcommand{\ps}{\mathcal{S}}
\renewcommand{\a}{_{\rm a}}
\newcommand{\s}{_{\rm s}}
\renewcommand{\d}{_{\rm d}}
\begin{document}

@@

A group of binarity-ignoring astronomers wants to measure the mean number of 
planets of a certain type per star of a certain type.
They perform a wide-field photometric search for planets that transit, and 
discover all for which
\begin{equation}
\left(\frac{{\rm S}}{{\rm N}}\right)
= ({\rm const}) \cdot \delta_{\rm obs} L_{\rm sys}^{1/2} d^{-1}
> \left(\frac{{\rm S}}{{\rm N}}\right)_{\rm floor}.
\label{eq:S_N_thresh}
\end{equation}
The observed transit depth $\delta_{\rm obs}$ constitutes the signal, ${\rm 
S}$. The survey is shot-noise dominated, and so the noise ${\rm N}$
scales as the inverse root of the photon flux received from any stellar 
system, ${\rm N} \propto (L_{\rm sys}/d^2)^{-1/2}$, for $L_{\rm sys}$ the 
system luminosity and $d$ its distance.
The solid angle coverage, telescope area, and survey duration are part of the 
``const'' term of Eq.~\ref{eq:S_N_thresh}. The transit duration also 
affects detectability, but we omit it in this work for brevity.

To compute an occurrence, at every planetary and stellar property the 
astronomers choose the stars (among those initially surveyed) around which the 
planets of interest appeared to be searchable.
Correcting for the geometric transit probability $p_{\rm tra}$, they report an 
apparent rate density,
\begin{equation}
\Gamma\a(\pp\a, \ps\a) = \frac{n_{\rm det}(\pp\a, \ps\a)}{N_{\rm s,a}(\pp\a, 
    \ps\a)} \times \frac{1}{p_{\rm tra}(\pp\a, \ps\a)}.
\label{eq:defn_apparent_rate_density}
\end{equation}
where $\pp\a$, $\ps\a$ are the apparent planetary and stellar parameters.
The quantity $N_{\rm s,a}(\pp\a, \ps\a)$ is the number of unresolved 
point-sources on the sky that appear to be searchable, and
$n_{\rm det}(\pp\a, \ps\a)$ is the number of detected planets, per unit 
$\pp\a$ and $\ps\a$.

@@

Here we focus on problems that arise from the fact that many stars exist in 
multiple star systems.
For simplicity, we consider only binaries, and we assume that they are all 
bound and spatially unresolved.

@@

Outside of astrophysical differences, every term in 
Eq.~\ref{eq:defn_apparent_rate_density} is observationally-biased.
There are errors in $n_{\rm det}(\pp\a,\ps\a)$ due to planet radius 
misclassification.
There are errors in $N_{{\rm s,a}}(\pp\a,\ps\a)$ because an apparently 
searchable point on the sky might include two searchable stars.
There are errors in $p_{\rm tra}(\pp\a,\ps\a)$ because stars in binaries may 
have different masses and radii than assumed in the single-star case.
Binarity might also affect the observers' ability to correctly select 
searchable stars (but see Sec.~\ref{sec:model_1} for discussion of this 
issue).

@@

To gain intuition for the many observational biases at play,
we consider a set of idealized transit surveys:
\begin{itemize}
    \item Model \#1: fixed stars, fixed planets, twin binaries;
    \item Model \#2: fixed planets and primaries, varying secondaries;
    \item Model \#3: fixed primaries, varying planets and secondaries.
\end{itemize}
In Sec.~\ref{sec:definitions}, we clarify our terminology and state
assumptions that apply throughout this study.
We then present our transit survey models in 
Secs.~\ref{sec:model_1}-\ref{sec:model_3}, where 
each subsection corresponds to a model listed above.
We interpret these calculations throughout, and in 
Sec.~\ref{sec:discussion} connect them to topical questions in 
the interpretation of transit survey occurrence rates.
In particular, we mention the ``hot Jupiter rate discrepancy'', the relevance 
towards measurements of $\eta_\oplus$, and the implications for detailed 
study of \citet{fulton_california-_2017}'s recently discovered ``valley''.
We conclude in Sec.~\ref{sec:conclusion}.

@@

\section{Definitions and Preliminaries}
\label{sec:definitions}

\subsection{Occurrence rate, occurrence rate density}
Define the occurrence rate density, $\Gamma$, as the expected number of 
planets per star per unit of planetary and stellar phase space.
Since we will mainly be concerned with the rate density's dependence on 
planetary radii $r$, we write
\begin{equation}
\Gamma(r) = \frac{{\rm d}\Lambda}{{\rm d}r},
\label{eq:rate_density_defn}
\end{equation}
where $\Lambda$ is the occurrence rate.
In this notation, ``the occurrence rate of planets of a particular size'' 
translates to an integral of Eq.~\ref{eq:rate_density_defn}, evaluated over a 
radius interval.

The above definition implicitly marginalizes the rate density over stellar 
multiplicity.
Considering only single and binary systems, the rate density for any selected 
sample of stars is a weighted sum of rate densities for each system type:
\begin{equation}
N_{\rm tot} \Gamma_{\rm sel}(r) =
N_0 \Gamma_0(r) +
N_1 \Gamma_1(r) +
N_2 \Gamma_2(r),
\label{eq:rate_density_marginalized}
\end{equation}
where $i=0$ corresponds to single stars, $i=1$ to primaries of 
binaries, and $i=2$ to secondaries of binaries.
$N_{\rm tot} = \sum_i N_i$ is the total number of selected stars, and 
$N_0,N_1,N_2$ are the number of selected single stars, primaries, and 
secondaries. For our purposes binary systems are not identifiable, and so 
$N_1=N_2$.

The rate density for each type of star, $\Gamma_i(r)$, can be written as 
the product of a shape function and a constant:
\begin{equation}
\Gamma_i(r) = \frac{{\rm d}\Lambda_i}{{\rm d}r} = Z_i f_i(r),
\quad {\rm for}\ i\in\{0,1,2\}.
\label{eq:rate_density_shape}
\end{equation}
The shape function is normalized to unity.
The $Z_i$'s can be interpreted as each system type's occurrence rate 
$\Lambda_i$, integrated over all planetary radii.
They are equivalent to the number of planets per single star, primary, or 
secondary.

\subsection{Searchable stars}
For a given planet radius, semimajor axis, and stellar luminosity, a fixed 
signal-to-noise floor yields a maximum searchable 
distance~\citep{pepper_using_2003,pepper_searching_2005}.
From Eq.~\ref{eq:S_N_thresh}, this maximum searchable distance scales as
\begin{equation}
d(\delta_{\rm obs}, L_{\rm sys}) \propto \delta_{\rm obs} \cdot L_{\rm 
    sys}^{1/2}.
\end{equation}
Assuming that stars are uniformly distributed in space, the number 
of searchable stars $N\s$ is then proportional to
\begin{equation}
N\s(\delta_{\rm obs}, L_{\rm sys}) \propto n \delta_{\rm obs}^3 L_{\rm 
    sys}^{3/2},
\label{eq:N_searchable_prop}
\end{equation}
where $n$ is the volume density of {\it e.g.}, single star, or binary systems.
We neglect the dependence of $n$ on stellar type.

\subsection{Relation between Apparent and Actual Stellar Properties}

We assume that the apparent properties of an unresolved binary are identical to
the true properties of the primary:
\begin{equation}
M\a=M_1, \quad R\a=R_1, ...
\end{equation}
We also take the stellar radius and luminosity to be uniquely related to the 
stellar mass.
Given these assumptions, the total luminosity of a system is
\begin{equation}
L_{\rm sys}=L_1+L_2=L(M\a)+L(qM\a),
\end{equation}
where $q=M_2/M_1$. Note that $L_{\rm sys}$ is the true value (because $M\a$ is 
the true primary mass), while an observer with no a priori knowledge of the 
distance to a system would measure a flux, assume a stellar mass $M_a$, and 
estimate a system luminosity of $L(M\a)$.

\subsection{Apparent number of searchable stars}
\label{subsec:apparent_N_searchable}

\begin{figure}[!tb]
    \centering
    \includegraphics[width=0.6\textwidth]{figures/mass_ratio_distribution.pdf}
    \caption{
        The mass ratio distribution for a magnitude-limited sample of 
        binary stars, in which the underlying volume-limited distribution is 
        uniform, qualitatively similar to {\it e.g.}, 
        \citet{raghavan_survey_2010}'s Fig.~16.
        At a given observed depth, the searchable binaries in a transit survey 
        are magnitude-limited (see Sec.~\ref{subsec:apparent_N_searchable}).
    }
    \label{fig:q_distribn_mag_limited}
\end{figure}

Given the observed signal $\delta_{\rm obs}$ and apparent stellar mass $M\a$, 
the maximum searchable distance for singles and binaries are proportional to 
$\delta_{\rm obs}\cdot L(M\a)^{1/2}$ and $\delta_{\rm obs}\cdot 
[L(M\a)+L(qM\a)]^{1/2}$.
Thus, the apparent number of searchable stars (points in the sky), which 
will be selected by an ignorant observer, can be written as
\begin{align}
N_{\rm s,a}(\delta_{\rm obs}, M\a)
= N\s^0(\delta_{\rm obs}, L(M\a)) \left[1+\mu(\mathrm{BF}, 
M\a)\right],
\label{eq:N_selected}
\end{align}
where $N\s^0$ is the number of searchable singles (this agrees with the actual 
value), $\mathrm{BF}=n_{\rm b}/(n_{\rm s}+n_{\rm b})$ 
is the binary fraction in a volume-limited sample,
$n_s$ ($n_b$) is the number density of single (binary) systems in a 
volume-limited sample,
and $\mu$ is the ratio of the number of double to single star 
systems that are searchable for an observed signal $\delta_{\rm obs}$.
Applying Eq.~\ref{eq:N_searchable_prop},
\begin{equation}
\mu({\rm BF},M\a) = 
{N_{\rm d} \over N_s^0}=
\int_0^1 {n_{\rm b}\over n_{\rm s}}\left[1+{L(qM\a) \over L(M\a)}\right]^{3/2} 
f(q)\mathrm{d}q,
\label{eq:mu_general}
\end{equation}
where $f(q)$ is the distribution of binary mass ratios in a volume-limited 
sample.
If $\mathrm{BF}$ is independent of $q$, $L \propto M^\alpha$, and $f(q) 
\propto q^\beta$, this reduces to
\begin{equation}
\mu =\frac{{\rm BF}}{1 - {\rm BF}}\cdot {1\over{1+\beta}}\int_0^1 
\left(1+q^\alpha\right)^{3/2} q^\beta\mathrm{d}q,
\end{equation}
which may be written in a closed form using the hypergeometric function.

This can be understood as a Malmquist bias: at fixed observed transit 
depth, for singles and primaries with the same luminosity, binaries are 
searchable to a greater distance.
In particular, the sample of searchable binaries is magnitude-limited.
Given a searchable binary, the probability of drawing a mass ratio $q$ will 
scale as
\begin{equation}
p({\rm draw\ }q\,|\,{\rm system\ is\ binary}) \propto 
(1+q^\alpha)^{3/2} q^\beta 
\label{eq:Malmquist_bias}
\end{equation}
where $q^\beta$ is the volume-limited probability of drawing a binary of mass 
ratio $q$, and the first term is the Malmquist bias.
We show this magnitude-limited mass ratio distribution for the $\beta=0$ case 
in Fig.~\ref{fig:q_distribn_mag_limited}.
In Monte Carlo simulations of transit surveys, it is 
important to draw binaries from a correctly biased mass-ratio distribution 
\citep[\textit{e.g.},][]{bakos_hatsouth:_2013,sullivan_transiting_2015,
    gunther_new_2017}.

@@

@@

\begin{figure}[!tb]
    \begin{center}
        \includegraphics[width=.6\textwidth]{figures/occ_rate_vs_radius_model_1_brokenx.pdf}
    \end{center}
    \vspace{-0.5cm}
    \caption{
        Inferred occurrence rates over $0.01r_\oplus$ bins in planet 
        radius, for Model \#1.
        This model has fixed stars, fixed planets, and twin binaries. 
        We assume a twin binary fraction of ${\rm BF}=0.1$, and that all 
        stars (single, primary, and secondary) host planets at equal 
        rates.
        If the true planet radius is $r_p$, all planets detected in binaries 
        will have apparent radii $r\a = r_p/\sqrt{2}$.
    }
    \label{fig:occ_rate_model_1}
\end{figure}

Since the effects of binarity are most pronounced when the two components are 
similar, we first consider a universe in which all planets are 
identical, and all stars are identical except that some fraction of them exist 
in binaries.
Expressed mathematically, from Eqs.~\ref{eq:rate_density_marginalized} 
and~\ref{eq:rate_density_shape} the rate density for a selected sample of 
stars at planet radius $r$ is
\begin{equation}
\Gamma_{\rm sel}(r) = \delta(r-r_p) \times
\frac{
    Z_0 +
    \mu (Z_1 + Z_2)
}{1+2\mu},
\label{eq:model_1_rate_density}
\end{equation}
where $\mu$ is given by Eq.~\ref{eq:mu_general} with $f(q) = \delta(q-1)$,
$\delta$ is the Dirac delta function, and the true planet radius is 
$r_p$.
We will generally write rate densities in terms of $\mu$'s, rather than 
$N_i$'s, because $\mu$'s are independent of planet radius.

We return to our group of binarity-ignoring astronomers. They select all the 
points on-sky that they think are searchable: those that are above some flux 
limit (at each $\delta_{\rm obs}$).
The relevant stellar samples are illustrated in Fig.~\ref{fig:model_1_volumes}.
At an apparent radius equal to the true radius ($r\a=r_p$), the observer 
thinks all stars are singles, with $d<d_0$.
In fact, binaries with $r\a=r_p$ are also searchable, out to $\sqrt{2}d_0$. 
However, in this model no such systems exist; all planets in twin binaries 
have true radii $r=r_p$, and so are observed with apparent radii 
$r\a=r_p/\sqrt{2}$.
This is because of ``radius dilution'':
for an unresolved point-source... %TODO FIXME

At an apparent radius of $r\a=r_p/\sqrt{2}$, there might also be planets with 
true radii $r=r_p/\sqrt{2}$ orbiting a single~---~however none of these exist 
in this model either.
Following Eq.~\ref{eq:defn_apparent_rate_density}, the apparent rate density 
computed without considering binarity is
\begin{equation}
\Gamma_a(r_a) = 
\frac{1}{1+\mu} Z_0 \cdot
\delta(r\a-r_p)  +
\frac{\mu}{1+\mu} (Z_1 + Z_2) \cdot
\delta\left(r\a-\frac{r_p}{\sqrt{2}} \right),
\label{eq:model_1_apparent_rate_density}
\end{equation}

The rate density for selected stars (Eq.~\ref{eq:model_1_rate_density}) and the
apparent rate density (Eq.~\ref{eq:model_1_apparent_rate_density}) differ in 
that (A) the total number of selected stars, $N_{\rm tot} = N_0+N_1+N_2$, was 
miscounted; and (B) the inferred radii in binary systems are all $\sqrt{2}$ 
too small.

To assess the severity of these errors, we need to assume a binary fraction, 
and to know the true number of planets per single, primary, and secondary star 
($Z_0,Z_1,$ and $Z_2$).
For the former,
\citet{raghavan_survey_2010} found a multiplicity 
fraction\footnote{
    The binary fraction is the fraction of systems in a volume-limited sample 
    that are binary. It is equivalent to the multiplicity fraction if there 
    are no triple, quadruple, or higher order multiples.
} of 0.44 for primaries with masses from $0.7M_\odot$ to $1.3M_\odot$. 
``Twin binaries'' are perhaps 10-20\% of the binaries in a volume-limited 
sample, depending on how ``twin'' is defined.
Thus a representative twin binary fraction for this model is ${\rm BF}\approx 
0.05$-$0.1$. 
For the latter, taking $Z_0=Z_1=Z_2=1/2$, we plot the resulting occurrence 
rates as a function of planet radius in Fig.~\ref{fig:occ_rate_model_1}.
When the $Z_i$'s are equal, the rate density for singles, $\Gamma_0(r)$ 
(dashed green line), is equal to the rate density for selected stars, 
$\Gamma_{\rm sel}(r)$ (solid orange line).

\paragraph{Correction to inferred rate density and inferred rate}
We can define a rate density ``correction factor'', $X_\Gamma$, as the ratio 
of the apparent to single star rate density,
\begin{equation}
X_\Gamma(r) \equiv \left. \frac{\Gamma_a(r\a)}{\Gamma_0(r)} \right|_{r\a 
\rightarrow r}.
\end{equation}
Continuing in the assumption that the number of planets per single, primary, 
and secondary star are equal, we find a rate density 
correction factor at the true planet radius of $1/(1+\mu)$.
This yields a correction of 0.76 if ${\rm BF}=0.1$, and 0.87 if ${\rm 
BF}=0.05$. Rephrasing the result, if the twin binary fraction were 
$(2^{3/2}+1)^{-1}\approx 0.26$, then the apparent rate would be half the true 
rate. Fortunately, in most contexts the twin binary fraction is not that high.

An alternative assumption is that secondaries do not host planets. In that 
case, $Z_0=Z_1$, and $Z_2=0$. The correction to the rate density at the true 
planet radius becomes $(1+2\mu)/(1+\mu)^2$.
This evaluates to 0.94 if ${\rm BF}=0.1$, and 0.98 if ${\rm BF}=0.05$.
While it seems unlikely that secondaries are planet-less, 
it is worth noting that $\Gamma_a/\Gamma$ is sensitive to the relative number 
of planets per single, primary, and secondary.

\paragraph{On completeness}
Our expressions for the apparent rate density 
(Eqs.~\ref{eq:defn_apparent_rate_density} 
and~\ref{eq:model_1_apparent_rate_density}) do not explicitly mention 
detection efficiency.
If we were to take a smooth detection probability in S/N, we would need to 
include an explicit detection efficiency term in 
Eq.~\ref{eq:defn_apparent_rate_density} is to inversely weight for planets 
that had low probabilities of being detected.
However, our ``detection probability'' is a step function in S/N 
(Eq.~\ref{eq:S_N_thresh}).
In our model, the maximum searchable distance is only a function of the 
apparent depth and true system luminosity.
Even though the observers are selecting stars based on what they think are 
``true radii'' (bottom row of Fig.~\ref{fig:model_1_volumes}), the 
actual searchability of a point-source is determined by apparent radius and 
system luminosity (Eq.~\ref{eq:S_N_thresh}; top rows of 
Fig.~\ref{fig:model_1_volumes}).
Thus at a given apparent radius $r\a$, the stars (single or binary) that are 
searchable are exactly the stars that are selected, since dilution affects the 
apparent radius and the maximum searchable distance in equal and opposite 
order.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Model \#2: Power law planets}
\label{sec:model_2}
